---
title: "linear_model"
output: html_document
date: "2023-11-09"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r, include = FALSE, message = FALSE, warning = FALSE}
library(tidyverse)
library(p8105.datasets)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


## load and clean the Airbnb data

```{r}
data("nyc_airbnb")

nyc_airbnb = 
  nyc_airbnb |> 
  mutate(stars = review_scores_location / 2) |> 
  rename(
    borough = neighbourhood_group,
    neighborhood = neighbourhood) |> 
  filter(borough != "Staten Island") |> 
  select(price, stars, borough, neighborhood, room_type)
```

Let's fit a model!!

```{r}
fit = 
  nyc_airbnb |>
  lm(price ~ stars + borough, data = _)
```

Let's look at the fit 

```{r}
fit
summary(fit)
coef(fit)
fitted.values(fit) #not recommended 
```

tidy up the output instead

```{r}
fit|>
  broom::glance()
```

tidy up the coefficient
```{r}
fit|>
  broom:: tidy()|>
  mutate(term = str_replace(term, "^borough", "Borough: ")) |>
  select(term, estimate, p.value) |>
  knitr::kable (digits = 3)
```

## Fit another model

```{r}
fit = 
  nyc_airbnb |>
  mutate(
    borough = fct_infreq(borough),
    room_type = fct_infreq(room_type)
  ) |>
  lm(price ~ stars + borough + room_type, data = _)

fit|>
  broom:: tidy()
```

## Quick look at diagnostics 

```{r}
nyc_airbnb|>
  modelr::add_residuals(fit) |> 
  ggplot(aes(x = resid)) +
  geom_density() +
  xlim(-100,500)
```

```{r}
nyc_airbnb|>
  modelr::add_residuals(fit) |> 
  ggplot(aes(x = borough, y = resid)) +
  geom_violin()
```

```{r}
nyc_airbnb|>
  modelr::add_residuals(fit) |> 
  ggplot(aes(x = stars, y = resid)) +
  geom_point()
```


## hypothesis test for categorical predictor 

fit a "null and "alternative model"

```{r}
fit_null = lm(price ~ stars + borough, data = nyc_airbnb)
fit_alternative = lm(price ~ stars + borough + room_type, data = nyc_airbnb)

anova(fit_null, fit_alternative) |>
  broom::tidy()
```

## borough-level differences

```{r}
fit = 
  nyc_airbnb |>
  lm(price ~ stars * borough + room_type * borough, data = _)

fit |>
  broom::tidy()
```

# goal is to fit 4 difference seperate linear model one for each borough and look at star effect

```{r}
airbnb_lm = function(df) {
  lm(price ~ stars + room_type, data = df)
  
}

nyc_airbnb |>
  nest(df = -borough) |>
  mutate(
    models = map(df, airbnb_lm),
    results = map (models, broom :: tidy)
  ) |>
  select(borough, results)|>
  unnest(results)|>
  select(borough, term, estimate) |>
  pivot_wider(
    names_from = term,
    values_from = estimate
  )|>
  knitr::kable(digits=2)
```

same things but just a little difference 

```{r}
nyc_airbnb |>
  nest(df = -borough) |>
  mutate(
    models = map(df, \(df) lm(price ~ stars + room_type, data = df)),
    results = map (models, broom :: tidy)
  ) |>
  select(borough, results)|>
  unnest(results)|>
  select(borough, term, estimate) |>
  pivot_wider(
    names_from = term,
    values_from = estimate
  )|>
  knitr::kable(digits=2)
```

## binary outcome
```{r}
baltimore_df = 
  read_csv("data/homicide-data.csv") |> 
  filter(city == "Baltimore") |> 
  mutate(
    resolved = as.numeric(disposition == "Closed by arrest"),
    victim_age = as.numeric(victim_age)) |> 
  select(resolved, victim_age, victim_race, victim_sex)
```

fitting a logistic regression 

```{r}
fit_logistic = 
  baltimore_df |>
  glm(resolved ~ victim_age + victim_race + victim_sex,
      data = _,
      family = binomial())
```

```{r}
fit_logistic|>
  broom::tidy()|>
  mutate(OR = exp(estimate)) |>
  select(term, estimate, OR)
```


